---
title: "STAT6190 - SGTA Topics G and H: Tests for Continuous and Categorical Variables"
author: "Ashwin Ravi"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    latex_engine: xelatex
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 4.5)
library(tidyverse)
library(knitr)
library(kableExtra)
```

---

# Introduction

This report analyses the **health.csv** dataset from STAT6190. The study investigates the effects of diet and exercise interventions (n = 1,500 participants) on a range of physiological, behavioural, and self-reported outcomes. Participants were assigned to three diet plans (Low Carb, Mediterranean, Intermittent Fasting) and three exercise regimens (Cardio, Strength, Mixed).

The report covers:

1. Exploratory Data Analysis (EDA) for variables relevant to the hypothesis tests.
2. Six hypothesis tests, with assumption checking and appropriate test selection.

---

# 1. Exploratory Data Analysis

```{r load-data}
health <- read.csv("health.csv")

# Derived variables used in tests
health <- health %>%
  mutate(
    chol_change    = cholesterol_after  - cholesterol_before,
    fitness_change = fitness_score_after - fitness_score_before,
    rt_change      = reaction_time_after - reaction_time_before
  )

dim(health)
```

## 1.1 Univariate Summaries

```{r univariate-summary}
vars_of_interest <- c("fitness_score_before", "weight_loss",
                      "chol_change", "fitness_change",
                      "reaction_time_before", "rt_change")

health %>%
  select(all_of(vars_of_interest)) %>%
  summary() %>%
  kable(caption = "Summary statistics for key variables") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

```{r eda-histograms, fig.height=8}
health_long <- health %>%
  select(all_of(vars_of_interest)) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value")

ggplot(health_long, aes(x = value)) +
  geom_histogram(bins = 40, fill = "steelblue", colour = "white", alpha = 0.8) +
  facet_wrap(~variable, scales = "free", ncol = 2) +
  labs(title = "Distributions of key continuous variables",
       x = NULL, y = "Count") +
  theme_minimal()
```

```{r eda-boxplots}
ggplot(health_long, aes(x = variable, y = value)) +
  geom_boxplot(fill = "steelblue", alpha = 0.7) +
  facet_wrap(~variable, scales = "free", ncol = 3) +
  labs(title = "Boxplots of key variables", x = NULL, y = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_blank())
```

**Observations:**

- `fitness_score_before` is centred close to 50 with a roughly symmetric, approximately normal shape.
- `weight_loss` is right-skewed; the majority of participants lost less than 5 kg.
- `chol_change` is strongly negative on average (cholesterol fell), with a near-symmetric distribution.
- `fitness_change` and `rt_change` are both centred away from zero, suggesting systematic improvement.
- `reaction_time_before` shows a clear bimodal pattern when all participants are pooled - foreshadowing the gender stratification analysis.

## 1.2 Reaction Time by Gender

```{r eda-rt-gender}
health %>%
  select(gender, reaction_time_before, reaction_time_after) %>%
  pivot_longer(-gender) %>%
  ggplot(aes(x = value, fill = gender)) +
  geom_histogram(bins = 40, alpha = 0.7, position = "identity") +
  facet_wrap(~name, scales = "free_x") +
  labs(title = "Reaction Time before and after, by gender",
       x = "Milliseconds", y = "Count", fill = "Gender") +
  scale_fill_manual(values = c("Female" = "coral", "Male" = "steelblue")) +
  theme_minimal()
```

```{r eda-rt-gender-stats}
health %>%
  group_by(gender) %>%
  summarise(
    n     = n(),
    mean_RT_before  = round(mean(reaction_time_before), 2),
    sd_RT_before    = round(sd(reaction_time_before), 2),
    mean_RT_after   = round(mean(reaction_time_after), 2),
    mean_RT_change  = round(mean(rt_change), 2)
  ) %>%
  kable(caption = "Reaction time summary by gender") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

The histograms confirm that males and females have markedly different reaction times (~231 ms vs ~321 ms), explaining the bimodal pattern in the pooled distribution.

---

# 2. Hypothesis Tests

All tests use a significance level of **alpha = 0.05**.

---

## 2.1 Is the fitness score before the study equal to 50?

**Hypotheses:**  
H0: mu = 50  
H1: mu != 50

**Assumption check - Normality:**

```{r q1-normality}
shapiro.test(sample(health$fitness_score_before, 500))
```

The Shapiro-Wilk test gives p = 0.28 (on a random sample of 500), so we do not reject normality. The sample is also large (n = 1,500), so the Central Limit Theorem further justifies the one-sample t-test.

```{r q1-test}
t.test(health$fitness_score_before, mu = 50)
```

**Conclusion:** t = 1.75, p = 0.081 > 0.05. We **fail to reject H0**. There is no statistically significant evidence that the mean fitness score before the study differs from 50. The sample mean of 50.4 is consistent with a true population mean of 50.

---

## 2.2 Is the mean weight loss different from 5 kg?

**Hypotheses:**  
H0: mu = 5  
H1: mu != 5

**Assumption check - Normality:**

```{r q2-normality}
shapiro.test(sample(health$weight_loss, 500))
ggplot(health, aes(x = weight_loss)) +
  geom_histogram(bins = 40, fill = "steelblue", colour = "white") +
  geom_vline(xintercept = 5, colour = "red", linetype = "dashed", linewidth = 1) +
  labs(title = "Weight loss distribution (red line = 5 kg)",
       x = "Weight loss (kg)", y = "Count") +
  theme_minimal()
```

The Shapiro-Wilk test gives p = 0.18; normality is plausible. With n = 1,500 the t-test is also robust to modest departures.

```{r q2-test}
t.test(health$weight_loss, mu = 5)
```

**Conclusion:** t = -58.2, p < 0.001. We **reject H0**. The mean weight loss (~ 3.63 kg) is highly significantly different from 5 kg. Participants lost substantially less than the 5 kg target on average.

---

## 2.3 Did participants improve their fitness scores after 8 weeks?

**Hypotheses (paired, directional):**  
H0: mu_after - mu_before = 0  
H1: mu_after - mu_before > 0

This is a **paired t-test** on `fitness_change = fitness_score_after - fitness_score_before`.

**Assumption check - Normality of differences:**

```{r q3-normality}
shapiro.test(sample(health$fitness_change, 500))
ggplot(health, aes(x = fitness_change)) +
  geom_histogram(bins = 40, fill = "steelblue", colour = "white") +
  geom_vline(xintercept = 0, colour = "red", linetype = "dashed", linewidth = 1) +
  labs(title = "Distribution of fitness score change",
       x = "Delta  Fitness score", y = "Count") +
  theme_minimal()
```

The Shapiro-Wilk test returns p < 0.001 for the differences, suggesting some departure from normality. However, with n = 1,500 the CLT ensures the sampling distribution of the mean is approximately normal, so the paired t-test remains valid.

```{r q3-test}
t.test(health$fitness_score_after, health$fitness_score_before,
       paired = TRUE, alternative = "greater")
```

**Conclusion:** t = 55.3, p < 0.001. We **reject H0**. There is very strong evidence that fitness scores improved after 8 weeks (mean improvement ~ 3.46 points).

---

## 2.4 Is the mean/median change in cholesterol significantly different from 0?

**Hypotheses:**  
H0: mu (or median) Delta cholesterol = 0  
H1: mu (or median) Delta cholesterol != 0

**Assumption check - Normality of differences:**

```{r q4-normality}
shapiro.test(sample(health$chol_change, 500))
ggplot(health, aes(x = chol_change)) +
  geom_histogram(bins = 40, fill = "steelblue", colour = "white") +
  geom_vline(xintercept = 0, colour = "red", linetype = "dashed", linewidth = 1) +
  labs(title = "Distribution of cholesterol change",
       x = "Delta  Cholesterol", y = "Count") +
  theme_minimal()
```

Shapiro-Wilk p = 0.032; there is mild evidence against normality. Given n = 1,500, the t-test is still appropriate via the CLT, but we also run the non-parametric **Wilcoxon signed-rank test** as a robustness check.

```{r q4-test}
# Parametric
t.test(health$chol_change, mu = 0)

# Non-parametric
wilcox.test(health$chol_change, mu = 0)
```

**Conclusion:** Both tests give p < 0.001 (t = -110.7; Wilcoxon V ~ 30). We **reject H0**. Cholesterol fell significantly during the study (mean change ~ -13.5 units). The result is robust to the mild non-normality.

---

## 2.5 Is the reaction time at enrolment equal to 275 ms?

### Why we need to stratify by gender

```{r q5-normality-all}
shapiro.test(sample(health$reaction_time_before, 500))

ggplot(health, aes(x = reaction_time_before, fill = gender)) +
  geom_histogram(bins = 50, alpha = 0.7, position = "identity") +
  geom_vline(xintercept = 275, colour = "black", linetype = "dashed", linewidth = 1) +
  scale_fill_manual(values = c("Female" = "coral", "Male" = "steelblue")) +
  labs(title = "Reaction time before study - pooled (bimodal) and by gender",
       x = "Reaction time (ms)", y = "Count", fill = "Gender") +
  theme_minimal()
```

The pooled distribution is strongly **bimodal** (Shapiro-Wilk p < 0.001), a direct consequence of males and females having very different mean reaction times (~231 ms vs ~321 ms). A single t-test on the pooled data would be **misleading**: the null hypothesis mu = 275 ms happens to sit near the midpoint of the two subgroup means, so the pooled test fails to reflect the reality for either group. **Stratification by gender is required.**

### Normality within gender subgroups

```{r q5-normality-by-gender}
shapiro.test(health$reaction_time_before[health$gender == "Male"])
shapiro.test(health$reaction_time_before[health$gender == "Female"])
```

Both subgroups are approximately normal (Male p = 0.92; Female p = 0.16), so a one-sample t-test is valid within each group.

### Tests by gender

**Hypotheses:**  
H0: mu = 275 ms  
H1: mu != 275 ms

```{r q5-test-male}
t.test(health$reaction_time_before[health$gender == "Male"], mu = 275)
```

```{r q5-test-female}
t.test(health$reaction_time_before[health$gender == "Female"], mu = 275)
```

**Conclusions:**

- **Males:** t = -59.1, p < 0.001. We **reject H0**. The mean male reaction time (~231 ms) is significantly *below* 275 ms.
- **Females:** t = 48.5, p < 0.001. We **reject H0**. The mean female reaction time (~321 ms) is significantly *above* 275 ms.

For both genders, reaction time at enrolment is significantly different from 275 ms, but in opposite directions - confirming that pooled inference would be invalid.

---

## 2.6 Has reaction time improved at the end of the study?

Improvement means a *decrease* in reaction time, so we test:

H0: mu_Delta  = 0  
H1: mu_Delta  < 0  (where Delta  = RT_after - RT_before)

### Normality of rt_change

```{r q6-normality-all}
shapiro.test(sample(health$rt_change, 500))
```

Shapiro-Wilk p = 0.36 for the pooled changes - normality holds. We also check within gender:

```{r q6-normality-by-gender}
shapiro.test(health$rt_change[health$gender == "Male"])
shapiro.test(health$rt_change[health$gender == "Female"])
```

Both subgroups are normal (Male p = 0.52; Female p = 0.18).

### Can we use the pooled cohort?

Unlike `reaction_time_before`, the **change scores** (`rt_change`) do not show a bimodal structure because both groups improved by similar amounts (Male mean ~ -15.0 ms; Female mean ~ -15.4 ms). The normality assumption is satisfied for the pooled changes, so we **can answer the question for the whole cohort**.

```{r q6-eda}
ggplot(health, aes(x = rt_change, fill = gender)) +
  geom_histogram(bins = 40, alpha = 0.7, position = "identity") +
  geom_vline(xintercept = 0, colour = "black", linetype = "dashed", linewidth = 1) +
  scale_fill_manual(values = c("Female" = "coral", "Male" = "steelblue")) +
  labs(title = "Distribution of reaction time change (RT_after - RT_before)",
       x = "Delta  Reaction time (ms)", y = "Count", fill = "Gender") +
  theme_minimal()
```

### Whole-cohort test

```{r q6-test-all}
t.test(health$rt_change, mu = 0, alternative = "less")
```

**Conclusion:** t = -57.3, p < 0.001. We **reject H0**. Reaction time improved significantly after 8 weeks for the cohort as a whole (mean decrease ~ 15.2 ms).

### By-gender tests (for completeness)

```{r q6-test-by-gender}
t.test(health$rt_change[health$gender == "Male"],   mu = 0, alternative = "less")
t.test(health$rt_change[health$gender == "Female"], mu = 0, alternative = "less")
```

Both males (t = -39.0, p < 0.001) and females (t = -42.1, p < 0.001) showed highly significant improvements individually, consistent with the pooled result.

---

# Summary of Results

```{r summary-table, echo=FALSE}
results <- data.frame(
  Question = c(
    "Fitness score before = 50?",
    "Mean weight loss != 5 kg?",
    "Fitness improved after 8 weeks?",
    "Cholesterol change != 0?",
    "RT before = 275 ms? (Male)",
    "RT before = 275 ms? (Female)",
    "RT improved? (whole cohort)"
  ),
  Test = c(
    "One-sample t-test",
    "One-sample t-test",
    "Paired t-test",
    "t-test + Wilcoxon",
    "One-sample t-test",
    "One-sample t-test",
    "One-sample t-test"
  ),
  Statistic = c(
    "t = 1.75",
    "t = -58.22",
    "t = 55.27",
    "t = -110.71",
    "t = -59.07",
    "t = 48.49",
    "t = -57.26"
  ),
  p.value = c(
    "0.081",
    "< 0.001",
    "< 0.001",
    "< 0.001",
    "< 0.001",
    "< 0.001",
    "< 0.001"
  ),
  Decision = c(
    "Fail to reject H0",
    "Reject H0",
    "Reject H0",
    "Reject H0",
    "Reject H0",
    "Reject H0",
    "Reject H0"
  ),
  stringsAsFactors = FALSE
)

kable(results,
      caption = "Summary of all hypothesis tests (alpha = 0.05)",
      booktabs = TRUE,
      col.names = c("Question", "Test", "Statistic", "p-value", "Decision")) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

---

# Topic H: Tests for One Categorical Variable

---

## EDA: Categorical Variables

### Satisfaction Ratings by Gender

```{r h-eda-satisfaction}
health %>%
  mutate(satisfaction = factor(satisfaction)) %>%
  ggplot(aes(x = satisfaction, fill = gender)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = c("Female" = "coral", "Male" = "steelblue")) +
  labs(title = "Satisfaction ratings by gender",
       x = "Satisfaction (1-5)", y = "Count", fill = "Gender") +
  theme_minimal()
```

```{r h-eda-satisfaction-table}
health %>%
  group_by(gender, satisfaction) %>%
  summarise(n = n(), .groups = "drop") %>%
  pivot_wider(names_from = satisfaction, values_from = n) %>%
  kable(caption = "Satisfaction counts by gender") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

### Weight Loss Success in Men on Low Carb Diet

```{r h-eda-weightloss}
health %>%
  filter(gender == "Male", diet == "Low Carb") %>%
  mutate(lost_weight = ifelse(weight_loss > 0, "Yes", "No")) %>%
  ggplot(aes(x = lost_weight, fill = lost_weight)) +
  geom_bar() +
  scale_fill_manual(values = c("Yes" = "steelblue", "No" = "coral")) +
  labs(title = "Weight loss success: Men on Low Carb diet",
       x = "Lost weight (weight_loss > 0)", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

```{r h-eda-weightloss-hist}
health %>%
  filter(gender == "Male", diet == "Low Carb") %>%
  ggplot(aes(x = weight_loss)) +
  geom_histogram(bins = 30, fill = "steelblue", colour = "white") +
  geom_vline(xintercept = 0, colour = "red", linetype = "dashed", linewidth = 1) +
  labs(title = "Weight loss distribution: Men on Low Carb diet",
       x = "Weight loss (kg)", y = "Count") +
  theme_minimal()
```

### Goal Achievement (met_goal)

```{r h-eda-metgoal}
health %>%
  mutate(met_goal = factor(met_goal, labels = c("Not met", "Met"))) %>%
  ggplot(aes(x = met_goal, fill = met_goal)) +
  geom_bar() +
  scale_fill_manual(values = c("Not met" = "coral", "Met" = "steelblue")) +
  labs(title = "Goal achievement across all participants",
       x = "Goal met (5 kg weight loss)", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

```{r h-eda-metgoal-table}
health %>%
  count(met_goal) %>%
  mutate(proportion = round(n / sum(n), 4),
         met_goal = factor(met_goal, labels = c("Not met (0)", "Met (1)"))) %>%
  kable(caption = "Goal achievement: observed counts and proportions",
        col.names = c("met_goal", "Count", "Proportion")) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

**Observations:**

- Satisfaction ratings for males appear roughly uniform across categories 1-5, though category 5 is slightly more frequent.
- The vast majority of men on the Low Carb diet (approx. 96\%) lost weight (weight_loss > 0).
- About 22.5\% of all participants met the 5 kg weight loss goal, slightly above the hypothesised 20\%.

---

## H.1 Do satisfaction ratings for men follow a uniform distribution?

**Hypotheses:**

- H0: Satisfaction ratings for men follow a Uniform(1/5, ..., 1/5) distribution
- H1: At least one category differs from the expected uniform proportion

Under H0, each of the 5 satisfaction levels is equally likely (p = 0.20 each).

```{r h1-eda}
men_sat <- health %>%
  filter(gender == "Male") %>%
  count(satisfaction) %>%
  arrange(satisfaction)

men_sat %>%
  mutate(expected = sum(n) / 5,
         proportion = round(n / sum(n), 3)) %>%
  kable(caption = "Observed and expected counts: Male satisfaction ratings",
        col.names = c("Satisfaction", "Observed", "Expected", "Proportion")) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

**Assumption check:** All expected counts = 150.4 (well above the minimum of 5 required for the chi-squared approximation to be valid).

```{r h1-test}
men_sat_counts <- health %>%
  filter(gender == "Male") %>%
  count(satisfaction) %>%
  arrange(satisfaction) %>%
  pull(n)

chisq.test(men_sat_counts)  # default: uniform expected probabilities
```

**Conclusion:** Chi-squared = 6.66, df = 4, p = 0.155 > 0.05. We **fail to reject H0**. There is no statistically significant evidence that male satisfaction ratings deviate from a uniform distribution. The slight overrepresentation of rating 5 (n = 172 vs expected 150.4) is within the range of random variation.

---

## H.2 Do at least 90\% of men on the Low Carb diet lose weight?

**Hypotheses (one-sided):**

- H0: p <= 0.90 (the true proportion losing weight is at most 90\%)
- H1: p > 0.90 (at least 90\% lose weight -- we test whether the evidence supports exceeding this threshold)

Note: The question asks whether at least 90\% lose weight. We frame this as a one-sided upper test: H0: p = 0.90 vs H1: p > 0.90. Rejecting H0 provides evidence that the proportion exceeds 90\%.

```{r h2-summary}
men_lc <- health %>%
  filter(gender == "Male", diet == "Low Carb") %>%
  mutate(lost_weight = weight_loss > 0)

n_lc   <- nrow(men_lc)
x_lc   <- sum(men_lc$lost_weight)
phat   <- x_lc / n_lc

cat("n =", n_lc, "\n")
cat("Successes (weight_loss > 0) =", x_lc, "\n")
cat("Sample proportion =", round(phat, 4), "\n")
```

**Assumption check:** np0 = 249 x 0.90 = 224.1 > 10 and n(1-p0) = 249 x 0.10 = 24.9 > 10. Normal approximation is valid.

```{r h2-test}
# z-test for one proportion: H0: p = 0.90, H1: p > 0.90
p0 <- 0.90
z_stat <- (phat - p0) / sqrt(p0 * (1 - p0) / n_lc)
p_val  <- pnorm(z_stat, lower.tail = FALSE)

cat("z =", round(z_stat, 4), "\n")
cat("p-value (one-sided, upper) =", round(p_val, 4), "\n")

# Also using prop.test for comparison
prop.test(x_lc, n_lc, p = 0.90, alternative = "greater", correct = FALSE)
```

**Conclusion:** z = 3.15, p = 0.0008 < 0.05. We **reject H0**. There is strong evidence that more than 90\% of men on the Low Carb diet successfully lose weight. The observed proportion of 95.98\% significantly exceeds the 90\% threshold.

---

## H.3 Is the proportion meeting their goals equal to 20\%?

**Hypotheses:**

- H0: p = 0.20
- H1: p != 0.20

```{r h3-summary}
n_total <- nrow(health)
n_met   <- sum(health$met_goal)
p_met   <- n_met / n_total

cat("n =", n_total, "\n")
cat("met_goal = 1:", n_met, "\n")
cat("Observed proportion:", round(p_met, 4), "\n")
```

### Chi-squared test

```{r h3-chisq}
obs <- c(n_met, n_total - n_met)
exp_props <- c(0.20, 0.80)
chisq.test(obs, p = exp_props)
```

### Binomial test

```{r h3-binom}
binom.test(n_met, n_total, p = 0.20, alternative = "two.sided")
```

### Comparison and comment

```{r h3-compare}
data.frame(
  Test       = c("Chi-squared", "Binomial"),
  Statistic  = c("X2 = 6.017", "---"),
  p.value    = c("0.0142", "0.0155"),
  Decision   = c("Reject H0", "Reject H0")
) %>%
  kable(caption = "Comparison: chi-squared and binomial tests for met goal = 20 pct",
        col.names = c("Test", "Statistic", "p-value", "Decision")) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

**Conclusion and comparison:**

Both tests give p < 0.05 and both **reject H0**, concluding that the proportion meeting the goal is significantly different from 20\%. The observed proportion is 22.53\%, slightly above the hypothesised 20\%.

The two p-values are very close (chi-squared: 0.0142; binomial: 0.0155) but not identical:

- The **chi-squared test** uses a large-sample normal approximation (valid here since np0 = 300 and n(1-p0) = 1200 are both >> 5). It is computationally simpler and equivalent to a squared z-test.
- The **binomial test** is exact -- it computes probabilities directly from the Binomial(1500, 0.20) distribution without any approximation. It is preferred when sample sizes are small or when the proportion is near 0 or 1.
- With n = 1,500 the approximation is excellent, hence the near-identical results. In general, the binomial test is the gold standard for one-proportion problems.

---

# Summary of All Results

```{r full-summary-table, echo=FALSE}
all_results <- data.frame(
  Topic = c(
    rep("G", 7),
    rep("H", 3)
  ),
  Question = c(
    "Fitness score before = 50?",
    "Mean weight loss != 5 kg?",
    "Fitness improved after 8 weeks?",
    "Cholesterol change != 0?",
    "RT before = 275 ms? (Male)",
    "RT before = 275 ms? (Female)",
    "RT improved? (whole cohort)",
    "Male satisfaction uniform?",
    ">= 90 pct Low Carb men lose weight?",
    "Prop. meeting goal = 20 pct?"
  ),
  Test = c(
    "One-sample t-test",
    "One-sample t-test",
    "Paired t-test",
    "t-test + Wilcoxon",
    "One-sample t-test",
    "One-sample t-test",
    "One-sample t-test",
    "Chi-squared GoF",
    "z-test (one proportion)",
    "Chi-squared + Binomial"
  ),
  p.value = c(
    "0.081", "< 0.001", "< 0.001", "< 0.001",
    "< 0.001", "< 0.001", "< 0.001",
    "0.155", "0.0008", "0.014 / 0.016"
  ),
  Decision = c(
    "Fail to reject H0",
    "Reject H0", "Reject H0", "Reject H0",
    "Reject H0", "Reject H0", "Reject H0",
    "Fail to reject H0",
    "Reject H0", "Reject H0"
  ),
  stringsAsFactors = FALSE
)

kable(all_results,
      caption = "Complete summary of hypothesis tests (Topics G and H, alpha = 0.05)",
      booktabs = TRUE,
      col.names = c("Topic", "Question", "Test", "p-value", "Decision")) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

---

# Appendix: Session Info

```{r session-info}
sessionInfo()
```
